Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-10-21 paper.tex
related work and improved search policy section

The second step involves generating a high-level program capable of producing the program trace identified by the first phase.
%In principle, we could also train a neural network to learn this mapping. In practice, though, this would be challenging because it would no longer be sufficient to train the network with a synthetic corpus of randomly generated programs, since our goal is to generate programs that satisfy certain semantic constraints that ensure that we get the program that the user most likely intended.
This paper argues that this stage is best achieved by \emph{constraint-based program synthesis} \cite{solar2008program}. Without the need for training, the program synthesizer can search the space of possible programs for one capable of producing the desired trace -- inducing structures like
symmetries, repetition, or conditional branches.
Although these program synthesizers do not \emph{need} any training data,
we show how to combine conventional machine learning with bias optimal search~\cite{schmidhuber2004optimal}
in order to synthesize complicated programs in only a few minutes.

@@

\noindent \textbf{The Trace Hypothesis.} The execution trace of a program
is the correct liaison between high-level structured symbolic representations
and high-dimensional unstructured perceptual input.

The roadmap of our paper is structured around the trace hypothesis, as outlined in Figure~\ref{roadmap}.
\begin{figure}
  \begin{tikzpicture}
    \node[ thick,anchor = west,inner sep=0pt,label=below:{\small Perceptual input}](observation) at (0,0) {\includegraphics[width = 1.5cm]{figures/expert-39-trimmed.png}};
    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Trace}](trace) at (3,0) {\includegraphics[width = 1.5cm]{../TikZ/drawings/expert-39-parses/0.png}};

@@

    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
    ([yshift = -15,xshift = -30]observation.south) -- node[below = 6pt] {Section~\ref{neuralNetworkSection}: Perception$\to$Trace} ([yshift = -15,xshift = -5]trace.south);
    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
    ([xshift = 5,yshift = -15]trace.south) -- node[below = 6pt] {Section~\ref{programSynthesisSection}: Trace$\to$Program} ([xshift = 140,yshift = -15]trace.south);
    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
([xshift = 150,yshift = -15]trace.south) -- node[below = 6pt] {Section~\ref{applicationsSection}: Applications} ([xshift = 250,yshift = -15]trace.south);
  \end{tikzpicture}
  \caption{Paper roadmap: Structured around the \emph{trace hypothesis}}\label{roadmap}
\end{figure}

%under a quantitative objective that maximizes the likelihood according to a prior distribution that aims to capture the user’s preference.

@@

Synthesizing programs from their execution traces is an old
idea~\cite{Summers:1977:MLP:321992.322002}.  This previous work
departs from our approach in the nature of the problem (synthesizing
recursive algorithms in Lisp vs. graphics programs in~\LaTeX) and the
specifics of the solution (hand-coded source-to-source transformations vs. neural networks
combined with general-purpose program synthesis techniques).
What they share is the use of an execution trace as a
stepping stone toward a full program.

@@

Figure~\ref{architecture} illustrates this architecture.  We first
pass a $256\times 256$ target image and a rendering of the trace so
far (encoded as a two-channel image) to a convolutional network. Given
the features extracted by the convnet, a multilayer perceptron then
predicts a distribution over the next drawing command to add to the
trace; see Table~\ref{drawingCommandTable}.  We predict the drawing
command token-by-token, conditioning each token both on the image
features and on the previously generated tokens. We also use a
differentiable attention mechanism (Spatial Transformer
Networks:~\cite{jaderberg2015spatial}) to let the model attend to
different regions of the image while predicting each token. For
example, the network first decides to emit the \verb|circle| token
conditioned on the image features, then it emits the $x$ coordinate of
the circle conditioned on the image features and the \verb|circle|
token, and finally it predicts the $y$ coordinate of the circle
conditioned on the image features, the \verb|circle| token, and the
$x$ coordinate. For our main experiments we constrain
coordinates to lie on a discrete $16\times 16$ grid, and later explain
how to remove this restriction.  See supplement for the full details
of the architecture, which we implemented in
Tensorflow~\cite{tensorflow2015-whitepaper}.
%% \remark{There are some more details that are important to provide
%%   about this architecture in the supplement: the
%%   functional form(s) of the probability distributions over tokens, the
%%   network layer sizes, which MLPs share parameters, etc.}

@@

%  \node at (canvas.x,canvas.y) {Canvas};
\end{tikzpicture}
\caption{Our neural architecture for inferring the execution trace of a graphics program from its output. \textcolor{blue}{Blue}: network inputs. Black: network operations. \textcolor{red}{Red}: samples from a multinomial. \texttt{Typewriter font}: network outputs. Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}. STN (spatial transformer network) is a differentiable attention mechanism~\cite{jaderberg2015spatial}.}  \label{architecture}
\end{figure}
\begin{table}[h]
\begin{tabular}{ll}\toprule
  \begin{tabular}{l}
    \verb|circle|$(x,y)$
  \end{tabular}& \begin{tabular}{l}
    Circle at $(x,y)$
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|rectangle|$(x_1,y_1,x_2,y_2)$
  \end{tabular}&\begin{tabular}{l}
    Rectangle with corners at $(x_1,y_1)$ \& $(x_2,y_2)$
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|line|$(x_1,y_1,x_2,y_2,$\\
    \hspace{1cm}$\text{arrow}\in\{0,1\},\text{dashed}\in\{0,1\})$
  \end{tabular}&\begin{tabular}{l}
    Line from $(x_1,y_1)$ to  $(x_2,y_2)$,\\\hspace{1cm}optionally with an arrow and/or dashed
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|STOP|
  \end{tabular}&\begin{tabular}{l}
    Finishes execution trace inference
    \end{tabular}
\\  \bottomrule
\end{tabular}
\caption{The deep network in Fig.~\ref{architecture} predicts drawing commands, shown above.}
\label{drawingCommandTable}
\end{table}

For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
\begin{equation}
  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
\end{equation}
where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
the target image, $T$ is an execution trace, $\theta$ are the
parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
execution traces factorizes as:
\begin{equation}
  \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
\end{equation}
where $|T|$ is the length of execution trace $T$, the subscripts
on $T$ index drawing commands within the trace, and the \verb|STOP|
token is emitted by the network to signal that the trace
explains the image.

@@

The constrained optimization problem in
Equation~\ref{programObjective} is intractable in general, but there
exist efficient-in-practice tools for finding exact solutions to such
program synthesis problems. We use the state-of-the-art Sketch
tool~\cite{solar2008program}. Describing Sketch's program synthesis
algorithm is beyond the scope of this paper; see~\cite{solar2008program}.  At a
high level, Sketch takes as input a space of programs, along with a
specification of the program's behavior and optionally a cost
function.  It translates the synthesis problem into a constraint
satisfaction problem and then uses a SAT solver to find a
minimum-cost program satisfying the specification.  In exchange for
having no guarantee on the time required to find a minimum
cost solution, it comes with the guarantee that it will always find a
globally optimal program.
In practice, synthesis times vary from a few minutes to a a few hours,
with 16\% of the diagrams timing out the synthesizer after 3 hours.
See Figure~\ref{exampleSynthesisResults} for examples of the kinds of programs our system recovers.
A main impediment here to our use of these general techniques is
the prohibitively high cost of searching for programs.

\subsection{Learning a search policy for synthesizing programs}

@@

An example of a $1$-bias optimal search algorithm is a time-sharing system
that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to testing $\sigma $.
We construct a $1$-bias optimal search algorithm for our domain by
identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |T)$
and $t(\sigma )  $ with how long the program synthesizer takes to search through the programs in $\sigma $.

@@

We contrast our learned search policy
with two alternatives (see Figure~\ref{policyEvaluation}):
(1) \emph{Sketch}, which poses the
entire problem wholesale to the Sketch program synthesizer;
and (2) an \emph{Oracle},
a policy which always picks the quickest to search $\sigma $
 also containing a minimum cost program.
Our approach improves upon Sketch by itself,
and comes close to the Oracle's performance.
Of course one could never construct such an Oracle,
because the agent does not know ahead of time which
$\sigma $'s contain minimum cost programs nor does it know how long each
$\sigma $ will take to search.

\begin{figure}
  \includegraphics[width = 12cm]{figures/policyComparison.png}
  \caption{$\infty = $ timeout}\label{policyEvaluation}
  \end{figure}

This generalizes and strengthens previous work: Levin
search~\cite{levin1973universal,solomonoff1984optimum} \&
OOPS~\cite{schmidhuber2004optimal}: theoretically appealing but
impractical; fails to leverage either techniques from machine learning
or from program synthesis. More of a mathematical framing and less of
an algorithm.  DeepCoder~\cite{BalGauBroetal16}: in addition to
picking what sort of primitives can go into a program, we are picking
the details of the search algorithm as well as how deep the algorithms
should search.  Main difference is that we identify this interesting
trade-off between tractability and probability of getting a solution.
TerpreT~\cite{gaunt2016terpret}: suggests that constraint solvers outperform gradient-based search techniques like those used in differentiable neural computers.

Two intuitions: want a model that prefers sketches that are likely to
contain a valid solution, but at the same time prefers sketches that
are easy to search.  In general these two preferences are at odds with
one another.  For example, a sketch which allows very long programs
and allows lots of primitives is extremely likely to contain a
shortest program -- but might also take hours for the synthesizer to
search through.

@@

We measure the similarity between two drawings by extracting features
of the best programs that describe them. Our features are counts of the number of times that different components in the
DSL were used (Table~\ref{DSL}).  We project these features down to a
2-dimensional subspace using primary component analysis
(PCA); see Fig.\ref{NMF}.  One could use many
alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
We used our learned distance metric between execution traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}). This reveals similarities between the objects in the drawings,
while missing similarities at the level of the program.
\begin{figure}[h]
\centering  \begin{minipage}{\textwidth}\centering
  \includegraphics[width = 0.69\textwidth]{figures/PCA.png}
  \includegraphics[width = 0.69\textwidth]{figures/PCA_improved.png}
    \caption{PCA on features of the programs that were synthesized for each drawing. Symmetric figures cluster to the right; ``loopy'' figures cluster to the left; complicated programs are at the top and simple programs are at the bottom.}    \label{NMF}
  \end{minipage} %\hfill
  \begin{minipage}{\textwidth}\centering
    \includegraphics[width = 0.69\textwidth]{figures/imageSimilarity.png} 
    \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
  \end{minipage}
\end{figure}

@@

>>>>

The second step involves generating a high-level program capable of producing the program trace identified by the first phase.
%In principle, we could also train a neural network to learn this mapping. In practice, though, this would be challenging because it would no longer be sufficient to train the network with a synthetic corpus of randomly generated programs, since our goal is to generate programs that satisfy certain semantic constraints that ensure that we get the program that the user most likely intended.
This paper argues that this stage is best achieved by \emph{constraint-based program synthesis} \cite{solar2008program}. The program synthesizer can search the space of possible programs for one capable of producing the desired trace -- inducing structures like
symmetries, repetition, or conditional branches.
Although these program synthesizers do not \emph{need} any training data,
we show how to combine conventional machine learning with bias optimal search~\cite{schmidhuber2004optimal}
in order to synthesize programs over an order of magnitude faster than constraint-based synthesis techniques alone.

@@

\noindent \textbf{The Trace Hypothesis.} The execution trace of a program
is the correct liaison between high-dimensional unstructured perceptual input and high-level structured symbolic representations.

The roadmap of our paper is structured around the trace hypothesis, as outlined in Figure~\ref{roadmap}.
\begin{figure}[h]
  \begin{tikzpicture}
    \node[ thick,anchor = west,inner sep=0pt,label=below:{\small Perceptual input}](observation) at (0,0) {\includegraphics[width = 1.5cm]{figures/expert-39-trimmed.png}};
    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Trace}](trace) at (3,0) {\includegraphics[width = 1.5cm]{../TikZ/drawings/expert-39-parses/0.png}};

@@

    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
    ([yshift = -15,xshift = -30]observation.south) -- node[below = 6pt] {Section~\ref{neuralNetworkSection}: Perception$\to$Trace} ([yshift = -15,xshift = -5]trace.south);
    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
    ([xshift = 5,yshift = -15]trace.south) -- node[below = 6pt] {Section~\ref{programSynthesisSection}: Trace$\to$Program} ([xshift = 140,yshift = -15]trace.south);
    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
([xshift = 150,yshift = -15]trace.south) -- node[below = 6pt] {Section~\ref{applicationsSection}: Applications} ([xshift = 250,yshift = -15]trace.south);
  \end{tikzpicture}
  \caption{Paper roadmap. Both the paper and the system pipeline are structured around the \emph{trace hypothesis}}\label{roadmap}
\end{figure}

Prior work addresses converting hand drawings to vectors~\cite{huang2017shape,Nishida:2016:ISU:2897824.2925951} and converting synthetic images to symbolic parses~\cite{nsd,DBLP:journals/corr/Beltramelli17}.
Our new contribution is an approach for
converting perceptual input to high-level programs.
%under a quantitative objective that maximizes the likelihood according to a prior distribution that aims to capture the user’s preference.

@@

@@

Figure~\ref{architecture} illustrates this architecture.  We first
pass a $256\times 256$ target image and a rendering of the trace so
far (encoded as a two-channel image) to a convolutional network. Given
the features extracted by the convnet, a multilayer perceptron then
predicts a distribution over the next drawing command to add to the
trace; see Table~\ref{drawingCommandTable} for the drawing commands we currently model.  We predict the drawing
command token-by-token,\footnote{A token is an atomic symbol  -- so the model is \emph{not} predicting lines of code character-by-character, but instead knows about the syntactic structure of primitive commands} conditioning each token both on the image
features and on the previously generated tokens. We also use a
differentiable attention mechanism (Spatial Transformer
Networks:~\cite{jaderberg2015spatial}) to let the model attend to
different regions of the image while predicting each token. For
example, the network first decides to emit the \verb|circle| token
conditioned on the image features, then it emits the $x$ coordinate of
the circle conditioned on the image features and the \verb|circle|
token, and finally it predicts the $y$ coordinate of the circle
conditioned on the image features, the \verb|circle| token, and the
$x$ coordinate. For our main experiments we constrain
coordinates to lie on a discrete $16\times 16$ grid, and later explain
how to remove this restriction.  See supplement for the full details
of the architecture, which we implemented in
Tensorflow~\cite{tensorflow2015-whitepaper}.
%% \remark{There are some more details that are important to provide
%%   about this architecture in the supplement: the
%%   functional form(s) of the probability distributions over tokens, the
%%   network layer sizes, which MLPs share parameters, etc.}

@@

%  \node at (canvas.x,canvas.y) {Canvas};
\end{tikzpicture}
\caption{Our neural architecture for inferring the execution trace of a graphics program from its output. \textcolor{blue}{Blue}: network inputs. Black: network operations. \textcolor{red}{Red}: samples from a multinomial. \texttt{Typewriter font}: network outputs. Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}. STN (spatial transformer network) is a differentiable attention mechanism~\cite{jaderberg2015spatial}.}  \label{architecture}
\end{figure}
\begin{table}[h]
\begin{tabular}{ll}\toprule
  \begin{tabular}{l}
    \verb|circle|$(x,y)$
  \end{tabular}& \begin{tabular}{l}
    Circle at $(x,y)$
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|rectangle|$(x_1,y_1,x_2,y_2)$
  \end{tabular}&\begin{tabular}{l}
    Rectangle with corners at $(x_1,y_1)$ \& $(x_2,y_2)$
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|line|$(x_1,y_1,x_2,y_2,$\\
    \hspace{1cm}$\text{arrow}\in\{0,1\},\text{dashed}\in\{0,1\})$
  \end{tabular}&\begin{tabular}{l}
    Line from $(x_1,y_1)$ to  $(x_2,y_2)$,\\\hspace{1cm}optionally with an arrow and/or dashed
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|STOP|
  \end{tabular}&\begin{tabular}{l}
    Finishes execution trace inference
    \end{tabular}
\\  \bottomrule
\end{tabular}
\caption{Primitive drawing commands currently supported by our model.}
\label{drawingCommandTable}
\end{table}

For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
\begin{equation}
  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
\end{equation}
where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
the target image, $T$ is an execution trace, $\theta$ are the
parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
execution traces factorizes as:
\begin{equation}
  \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
\end{equation}
where $|T|$ is the length of execution trace $T$, the subscripts
on $T$ index drawing commands within the trace (so $T_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
token is emitted by the network to signal that the trace
explains the image.

@@

The constrained optimization problem in
Equation~\ref{programObjective} is intractable in general, but there
exist efficient-in-practice tools for finding exact solutions to such
program synthesis problems. We use the state-of-the-art Sketch
tool~\cite{solar2008program}. Describing Sketch's program synthesis
algorithm is beyond the scope of this paper; see~\cite{solar2008program}.  At a
high level, Sketch takes as input a space of programs, along with a
specification of the program's behavior and optionally a cost
function.  It translates the synthesis problem into a constraint
satisfaction problem and then uses a SAT solver to find a
minimum-cost program satisfying the specification.  In exchange for
having no guarantee on the time required to find a minimum
cost solution, it comes with the guarantee that it will always find a
globally optimal program.
In practice, synthesis times vary from minutes to hours,
with 16\% of the diagrams timing out the synthesizer after 3 hours.
See Figure~\ref{exampleSynthesisResults} for examples of the kinds of programs our system recovers.
A main impediment to our use of these general techniques is
the prohibitively high cost of searching for programs.
We next describe how to learn to synthesize programs much faster (Section~\ref{learningASearchPolicy}).

\subsection{Learning a search policy for synthesizing programs}\label{learningASearchPolicy}

@@

An example of a $1$-bias optimal search algorithm is a time-sharing system
that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
We construct a $1$-bias optimal search algorithm for our domain by
identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |T)$
and $t(\sigma )  $ with how long the program synthesizer takes to search through the programs in $\sigma $.

@@

We contrast our learned search policy
with two alternatives (see Figure~\ref{policyEvaluation}):
(1) \emph{Sketch}, which poses the
entire problem wholesale to the Sketch program synthesizer;
and (2) an \emph{Oracle},
a policy which always picks the quickest to search $\sigma $
 also containing a minimum cost program.
Our approach improves upon Sketch by itself,
and comes close to the Oracle's performance.
Of course one could never construct this Oracle,
because the agent does not know ahead of time which
$\sigma $'s contain minimum cost programs nor does it know how long each
$\sigma $ will take to search.

\begin{figure}
\centering  \includegraphics[width = 14cm]{figures/policyComparison.png}
  \caption{How long does it typically take to synthesize a minimum cost program? Sketch: out-of-the-box performance of the Sketch~\cite{solar2008program} program synthesizer. Oracle: baseline that always picks the easiest synthesis problem containing a minimum cost program. Learned policy: a bias-optimal learned search policy. Oracle is impossible to implement and is an upper bound on the performance of any search policy. $\infty = $ timeout. Red dashed line is median time.}\label{policyEvaluation}
  \end{figure}

@@

We measure the similarity between two drawings by extracting features
of the best programs that describe them. Our features are counts of the number of times that different components in the
DSL were used (Table~\ref{DSL}).  We project these features down to a
2-dimensional subspace using primary component analysis
(PCA); see Fig.\ref{NMF}.  One could use many
alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
We used our learned distance metric between execution traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}). This reveals similarities between the objects in the drawings,
while missing similarities at the level of the program.
\begin{figure}[h]
\centering  \begin{minipage}{\textwidth}\centering
  %\includegraphics[width = 0.69\textwidth]{figures/PCA.png}
  \includegraphics[width = 0.69\textwidth]{figures/PCA_improved.png}
    \caption{PCA on features of the programs that were synthesized for each drawing. Symmetric figures cluster to the right; ``loopy'' figures cluster to the left; complicated programs are at the top and simple programs are at the bottom.}    \label{NMF}
  \end{minipage} %\hfill
  \begin{minipage}{\textwidth}\centering
    \includegraphics[width = 0.69\textwidth]{figures/imageSimilarity.png} 
    \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
  \end{minipage}
\end{figure}

@@

Our approach to learning to search for programs draws theoretical
underpinnings from Levin
search~\cite{levin1973universal,solomonoff1984optimum} and
Schmidhuber's OOPS model~\cite{schmidhuber2004optimal}.
DeepCoder~\cite{BalGauBroetal16} and~\cite{menon2013machine} are
recent models which, like ours, learn to predict which program
components are likely to be useful given a program synthesis problem.
Our work is different from their approaches because we treat the
problem as a variety of \emph{metareasoning}, identifying and modeling
the trade-off between tractable search and probability of successful
search.  TerpreT~\cite{gaunt2016terpret} was the first work to
systematically compare constraint-based program synthesis techniques
against gradient-based search techniques (e.g., a
DNC~\cite{graves2016hybrid}).  The TerpreT experiments help motivate
our use of constraint-based techniques.

The idea that an execution trace could assist in program learning goes back to the 1970's~\cite{Summers:1977:MLP:321992.322002} and has also been applied in neural models of program induction, like Neural Program Interpreters~\cite{DBLP:journals/corr/ReedF15}.
Our contribution to this idea is the trace hypothesis:
that execution traces can be inferred from perceptual data,
and that the trace is the correct bridge between perception and symbolic representation.
Our work is the first to articulate and explore this hypothesis
by demonstrating how a trace could be inferred and how it can be used to synthesize a high-level program.
